### 2022-05-12 supplement.Rmd
Small tweaks to the supplementary tables, funnel

Next, we used selection models to approximate the selection process of experiments into the meta-analysis under the assumption that experiments that observe significant effects (i.e., with low p-values) are more likely to get published. We ran one selection model assuming a weight function with fixed p-value cutoffs at p = .01, p = .05, and p = 0.3[@vevea1995], as well as multiple models with a priori selection functions that assume bias of varying severity [@vevea2005]. These analyses show that our results are robust to small to medium amounts of publication bias (Supplementary Tables 8 and 9).

@@

```{r, tabs1, include=TRUE}
# Save within-analysis table of experiments
dat %>%
  mutate(
    age_mean = print_days_months(age_mean),
    age_sd = str_c(as.character(round(age_sd)), "d"),
  ) %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group_long,
    `Sample size` = sample_size,
    `Females` = round(female_percent * sample_size),
    Age = str_c(age_mean, "±", age_sd, sep = " "),
    Task = task,
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = stimuli_dimensions
  ) -> tabs1

@@

```{r, jackknife, include=TRUE}
# Re-run the jackknife analysis only if requested
if (run$jackknife_analysis) {

  # Re-fit the meta-analysis, leaving one experiment out at a time
  # Using parallelization with `furrr`
  n_cores <- availableCores()
  n_workers <- n_cores %/% n_chains
  plan(multisession, workers = n_workers)
  future_map_dfr(seq_len(nrow(dat)), function(jackknife_index) {
    dat_jackknife <- dat[-jackknife_index, ]
    res_jackknife <- update(res_brm, newdata = dat_jackknife, refresh = 0)
    print_res_table(
      res_jackknife,
      label_1 = dat$article[jackknife_index],
      label_2 = dat$group_long[jackknife_index],
      label_col_1 = "Article", label_col_2 = "Experiment"
    )
  }) -> tab_jackknife

  # Save the table
  write_csv(tab_jackknife, file = here(tables_dir, "jackknife.csv"))
} else {

  # Otherwise we load the pre-computed results
  tab_jackknife <- read_csv(
    here(tables_dir, "jackknife.csv"),
    col_types = "c", na = character()
  )
}

@@

```{r, primsa_checklist, include=TRUE}
# Read the CSV file
tab_prisma <- read_csv(
  here(data_dir, "prisma_checklist.csv"),
  col_types = "cic"
)

@@

```{r, sensitivity_analysis, include=TRUE}
# Re-run the sensitivity analyses only if requested
if (run$sensitivity_analysis) {

@@

  # Create table for the meta-analysis of gender differences
  sens %>%
    filter(!map_lgl(res_gender, is.null)) %>%
    select(res_gender, manipulation_name, manipulation_value) %>%
    pmap_dfr(function(res_gender, manipulation_name, manipulation_value) {
      print_res_table(
        res_gender,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tab_sens_gender
  write_csv(tab_sens_gender, file = here(tables_dir, "sens_gender.csv"))
} else {

  # Otherwise we load the pre-computed results
  tab_sens <- read_csv(
    here(tables_dir, "sens.csv"),
    col_types = "c", na = character(), trim_ws = FALSE
  )
  tab_sens_reg <- read_csv(
    here(tables_dir, "sens_reg.csv"),
    col_types = "c", na = character(), trim_ws = FALSE
  )
  tab_sens_gender <- read_csv(
    here(tables_dir, "sens_gender.csv"),
    col_types = "c", na = character(), trim_ws = FALSE
  )
}

# Display the tables
apa_table(
  tab_sens,
  caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
  font_size = "scriptsize", escape = FALSE
)
apa_table(
  tab_sens_reg,
  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
  font_size = "scriptsize", landscape = TRUE, escape = FALSE
)
apa_table(
  tab_sens_gender,
  caption = "Sensitivity analyses for the meta-analysis of gender differences",
  font_size = "scriptsize", escape = FALSE
)
```

@@

# Save the tables
write_csv(
  tabs_trim_fill_selection$meta,
  file = here(tables_dir, "trim_fill_selection_meta.csv")
)
write_csv(
  tabs_trim_fill_selection$gender,
  file = here(tables_dir, "trim_fill_selection_gender.csv")
)

# Display the tables
apa_table(
  tabs_trim_fill_selection$meta,
  align = "llccccc",
  caption = "Trim-and-fill and selection models for the meta-analysis of mental rotation performance",
  font_size = "scriptsize",
  escape = FALSE
)
apa_table(
  tabs_trim_fill_selection$gender,
  align = "llccccc",
  caption = "Trim-and-fill and selection models for the meta-analysis of gender differences",
  font_size = "scriptsize",
  escape = FALSE
)
```

@@

  # Add new funnel on top of the original funnel plot
  trim_fill_color <- "#e42536"
  plot +
    # Add trim and fill funnel
    geom_path(
      data = funnel_trim_fill,
      aes(x = x, y = y),
      color = trim_fill_color
    ) +
    geom_vline(xintercept = res$b, color = trim_fill_color) +
    # Add filled in studies
    geom_point(
      data = with(res, tibble(gi = yi[fill], sei = sqrt(vi[fill]))),
      color = trim_fill_color, shape = 0
    )
}) -> plots_funnel_trim_fill

@@

(ref:figs4-caption) **Trim-and-fill analyses.** As in Figure 3 in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance **(a)** and in the meta-analysis of gender differences within each article **(b)**. The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect sizes (vertical black lines). Gray shades indicate 95% pseudo-confidence intervals (dark gray) and 99% pseudo-confidence intervals (light gray) under the null hypothesis. Red squares show (fictional) experiments that were imputed via the trim-and-fill analyses, compensating for the small publication bias observed in the original funnel plots. Red lines show the meta-analytic effect sizes and its 95% pseudo-confidence interval for the trim-and-fill-corrected meta-analyses.

>>>>

Next, we used selection models to approximate the selection process of experiments into the meta-analysis under the assumption that experiments that observe significant effects (i.e., with low p-values) are more likely to get published. We ran one selection model assuming a weight function with fixed *p*-value cutoffs [@vevea1995] at *p* = .01, *p* = .05, and *p* = .30, as well as multiple models with a priori selection functions that assume bias of varying severity [@vevea2005]. These analyses show that our results are robust to small to medium amounts of publication bias (Supplementary Tables 8 and 9).

@@

```{r, tabs1, include=TRUE}
# Save within-analysis table of experiments
dat %>%
  mutate(
    age_mean = print_days_months(age_mean),
    age_sd = str_c(as.character(round(age_sd)), "d"),
  ) %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group_long,
    `Sample size` = as.integer(sample_size),
    `Females` = as.integer(round(female_percent * sample_size)),
    Age = str_c(age_mean, "±", age_sd, sep = " "),
    Task = task,
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = stimuli_dimensions
  ) -> tabs1

@@

```{r, jackknife}
# Re-run the jackknife analysis only if requested
if (run$jackknife_analysis) {

  # Re-fit the meta-analysis, leaving one experiment out at a time
  # Using parallelization with `furrr`
  n_cores <- availableCores()
  n_workers <- n_cores %/% n_chains
  plan(multisession, workers = n_workers)
  future_map_dfr(seq_len(nrow(dat)), function(jackknife_index) {
    dat_jackknife <- dat[-jackknife_index, ]
    res_jackknife <- update(res_brm, newdata = dat_jackknife, refresh = 0)
    print_res_table(
      res_jackknife,
      label_1 = dat$article[jackknife_index],
      label_2 = dat$group_long[jackknife_index],
      label_col_1 = "Article", label_col_2 = "Experiment"
    )
  }) %>%
    # Show article labels only for the first experiment per article
    mutate(
      Article = if_else(Article == lag(Article, default = ""), "", Article),
    ) -> tab_jackknife

  # Save the table
  write_csv(tab_jackknife, file = here(tables_dir, "jackknife.csv"))
}
```

```{r, tabs3, include=TRUE}
# Read jackknife table from file
tab_jackknife <- read_csv(
  here(tables_dir, "jackknife.csv"),
  col_types = "c", na = character()
)

@@

```{r, tabs4, include=TRUE}
# Read PRISMA checklist from file
tab_prisma <- read_csv(
  here(data_dir, "prisma_checklist.csv"),
  col_types = "ccc"
)

@@

```{r, sensitivity_analysis}
# Re-run the sensitivity analyses only if requested
if (run$sensitivity_analysis) {

@@

  # Create table for the meta-analysis of gender differences
  sens %>%
    filter(!map_lgl(res_gender, is.null)) %>%
    select(res_gender, manipulation_name, manipulation_value) %>%
    pmap_dfr(function(res_gender, manipulation_name, manipulation_value) {
      print_res_table(
        res_gender,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tab_sens_gender
  write_csv(tab_sens_gender, file = here(tables_dir, "sens_gender.csv"))
}
```

```{r, tabs5, include=TRUE}
# Load sensitivity analysis table from file
tab_sens <- read_csv(
  here(tables_dir, "sens.csv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

# Display the table
apa_table(
  tab_sens,
  caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
  font_size = "scriptsize", escape = FALSE
)
```

```{r, tabs6, include=TRUE}
# Load sensitivity analysis table from file
tab_sens_reg <- read_csv(
  here(tables_dir, "sens_reg.csv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

# Display the table
apa_table(
  tab_sens_reg,
  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
  font_size = "scriptsize", landscape = TRUE, escape = FALSE
)
```

```{r, tabs7, include=TRUE}
# Load sensitivity analysis table from file
tab_sens_gender <- read_csv(
  here(tables_dir, "sens_gender.csv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

# Display the table
apa_table(
  tab_sens_gender,
  caption = "Sensitivity analyses for the meta-analysis of gender differences",
  font_size = "scriptsize", escape = FALSE
)
```

@@

# Save the tables
write_csv(
  tabs_trim_fill_selection$meta,
  file = here(tables_dir, "trim_fill_selection_meta.csv")
)
write_csv(
  tabs_trim_fill_selection$gender,
  file = here(tables_dir, "trim_fill_selection_gender.csv")
)
```

```{r, tabs8, include=TRUE}
# Display the table
apa_table(
  tabs_trim_fill_selection$meta,
  align = "llccccc",
  caption = "Trim-and-fill and selection models for the meta-analysis of mental rotation performance",
  font_size = "scriptsize",
  escape = FALSE
)
```

```{r, tabs9, include=TRUE}
# Display the table
apa_table(
  tabs_trim_fill_selection$gender,
  align = "llccccc",
  caption = "Trim-and-fill and selection models for the meta-analysis of gender differences",
  font_size = "scriptsize",
  escape = FALSE
)
```

@@

  # Add new funnel on top of the original funnel plot
  trim_fill_color <- ifelse(sum(res$fill) >= 1, "#e42536", NA)
  plot +
    # Add trim and fill funnel
    geom_path(
      data = funnel_trim_fill,
      aes(x = x, y = y),
      color = trim_fill_color
    ) +
    geom_vline(xintercept = res$b, color = trim_fill_color) +
    # Add filled in studies
    geom_point(
      data = with(res, tibble(gi = yi[fill], sei = sqrt(vi[fill]))),
      color = trim_fill_color, shape = 0
    )
}) -> plots_funnel_trim_fill

@@

(ref:figs4-caption) **Trim-and-fill analyses.** As in Figure 3 in the main text, black squares indicate the effect sizes (x-axis) and standard errors (y-axis) of the individual experiments included in the meta-analysis of mental rotation performance **(a)** and in the meta-analysis of gender differences within each article **(b)**. The funnel contours (diagonal black lines) depict a 95% pseudo-confidence interval around the meta-analytic effect sizes (vertical black lines). Gray shades indicate 95% pseudo-confidence intervals (dark gray) and 99% pseudo-confidence intervals (light gray) under the null hypothesis. Red squares show (fictional) experiments that were imputed via the trim-and-fill analyses, compensating for the small publication bias observed in the original funnel plots. Red lines show the meta-analytic effect sizes and its 95% pseudo-confidence interval for the trim-and-fill-corrected meta-analyses. Note that for the meta-analysis of gender differences, the trim-and-fill analysis suggested that no additional experiments had to be imputed.
